A formalization of semi-simplicial and semi-cubical sets

### 2023-01-06 paper/paper.tex
.gitmodules: fix submodule url
paper: remove one def of \DeltaPlus

\begin{notation}[$\uparrow$]
  Let us write $\uparrow \{i_1, \ldots, i_n\}$ to denote $\{i_1 + 1, \ldots, i_n + 1\}$.
\end{notation}

\begin{definition}[\DeltaPlus]
  The category of augmented semi-simplices is defined in terms of objects, morphisms, composition, and identity.

  \begin{align*}
    \obj(\DeltaPlus) & := \Nat                                                                    \\
    \hom(p, n)       & := \{\{i_{p + 1}, \ldots, i_n\} \mid 0 < i_{p + 1} < \ldots < i_n \leq n\} \\
    g \circ f        & :=
    \begin{cases}
      g                          & \text{if f = \{\}}                                          \\
      f                          & \text{if g = \{\}}                                          \\
      b :: (g \circ f')          & \text{if $g = (a :: g')$, $f = (b :: f')$, with $b < a$}    \\
      a :: (g' \circ \uparrow f) & \text{if $g = (a :: g')$, $f = (b :: f')$, with $b \geq a$} \\
    \end{cases}      \\
    \id              & := \{\}
  \end{align*}

  Evidently, $\id$ is neutral. Further, composition can be shown to be associative.
\end{definition}

\begin{definition}[Alternative definition of $\DeltaPlus$]
  \begin{align*}
    \obj(\DeltaPlus) & := \Nat                                                                     \\
    \hom(p, n)       & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in l = p}\}        \\
    g \circ f        & :=
    \begin{cases}
      f                  & \text{if $g = \{\}$}                                                      \\
      0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
    \end{cases} \\
    \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times}
  \end{align*}

@@

Standard $n$-semi-cubes have a geometric interpretion, which we illustrate for dimensions $0$, $1$, and $2$.

>>>>

\begin{definition}[$\DeltaPlus$]
  \begin{align*}
    \obj(\DeltaPlus) & := \Nat                                                                     \\
    \hom(p, n)       & := \{l \in \{0, \kstar\}^n \mid \text{number of $\kstar$ in l = p}\}        \\
    g \circ f        & :=
    \begin{cases}
      f                  & \text{if $g = \{\}$}                                                      \\
      0 :: (g' \circ f)  & \text{if $g = (0 :: g')$}                                                 \\
      a :: (g' \circ f') & \text{if $g = (\star :: g')$, $f = (a :: f')$, where $a = 0$ or $\kstar$} \\
    \end{cases} \\
    \id              & := \{\kstar, \ldots, \kstar\} \text{ $n$ times}
  \end{align*}

@@

Standard $n$-semi-cubes have a geometric interpretation, which we illustrate for dimensions $0$, $1$, and $2$.
